---
  title: "inscriptions"
output: html_document
---
  
  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load inscriptions from EDCS&EDH

At SDAM project, we have prepared inscriptions dataset in json format on the basis of EDCS & EDH. 

You can load the json data with Sciencedata.dk login credentials. 
```{r libraries, include=FALSE}
#devtools::install_github("sdam-au/sdam")

library(tidyverse)
library(sdam)
library(jsonlite)
library(getPass)
```

1. Input your sciencedata.dk username - type directly into the RStudio console

```{r, login1, echo = FALSE }
user <- readline("your sciencedata username: ")
```

2. Make the request (you will be asked for password in a new pop-up window)

```{r, login2-request, echo = FALSE }
resp = request("EDHCS_v1-0.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/social_diversity", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```
Now you can move to the next step and make a tibble from the request's resp.

3. Make a tibble from the request and display the first six records

```{r inscriptions-json-wrangle}
list_json <- jsonlite::fromJSON(resp)
inscriptions = as_tibble(list_json)

interim_json <- jsonlite::toJSON(inscriptions, auto_unbox = TRUE)
list_json <- jsonlite::fromJSON(interim_json)
inscriptions = as_tibble(list_json)
head(inscriptions)
```


4. Make inscriptions into an `sf` object
IS PROVING DIFFICULT AS THE LATITUDE LONGITUDE COLUMNS ARE NOT NORMALIZED. REQUEST SENT TO VOJTECH!continue here.

```{r inscriptions-sf}
library(sf)
library(raster)
library(tidyverse)

tail(names(inscriptions))
inscriptions %>% 
  unlist(inscriptions$Latitude)
head(inscriptions$Latitude)
hist(inscriptions$pop_est)

library(mapview)
library(sf)

i <-  inscriptions %>% 
  select(id, Longitude, Latitude, not_before, type_of_inscription_clean) %>%  
  st_as_sf(coords = c(Longitude, Latitude), crs = 4326)
names(i)
n
```

# Read EDCHS merged dataset geojson directly with sf library
This 
```{r}
library(sf)
sample <- st_read("https://sciencedata.dk/public/a9237c5ea642d4714bcdefb03f70a1f4/EDHCSg.geojson")
```

```{r}
names(sample)
library(mapview)
mapview(sample)
```

